Screening Sinkhorn Algorithm for Regularized Optimal Transport

### 2019-05-21 tex/v3/section_3_algorithm.tex
update sec 3

\begin{wrapfigure}{o}{0.44\textwidth}
\vspace{-18pt}
\centering
\includegraphics[width=0.46\textwidth]{./figs/kappa_epsilon.pdf}
\caption{Plots of $\varepsilon$ and $\kappa$ as a functions of budgets for a screening test with $n_b=m_b$ and the parameters $\mu, \nu, \eta, C$ as in Figure~\eqref{fig:motivations}. As can be seen, $(\varepsilon, \kappa)$ tends to $(0,1)$ as $(n_b,m_b)$ tends to $(n,m)$.}
\label{fig:kappa_epsilon}
\vspace{-15pt}
\end{wrapfigure}

@@

Pseudocode of our proposed algorithm is shown in Algorithm~\ref{screenkhorn}. %~\cite{nocedal1980,nocedal2006numerical}
It is worth to note that Screenkhorn algorithm uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$ for calculating the objective function $\Psi_{\varepsilon, \kappa}$ and its gradients, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
Furthermore, it consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
The second is a constrained LBFGS for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}),$ 
that handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of Screenkhorn.

>>>>

\begin{wrapfigure}{o}{0.44\textwidth}
\vspace{-18pt}
\centering
\includegraphics[width=0.46\textwidth]{./figs/kappa_epsilon.pdf}
\caption{Plots of $\varepsilon$ and $\kappa$ as a functions of number budget of points for a screening test with $n_b=m_b$ and the parameters $\mu, \nu, \eta, C$ are setting as in Figure~\eqref{fig:motivations}. As can be seen, $(\varepsilon, \kappa)$ tends to $(0,1)$ as $(n_b,m_b)$ tends to $(n,m)$.}
\label{fig:kappa_epsilon}
\vspace{-15pt}
\end{wrapfigure}

@@

Pseudocode of our proposed algorithm is shown in Algorithm~\ref{screenkhorn}. %~\cite{nocedal1980,nocedal2006numerical}
It is worth to note that Screenkhorn algorithm uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$ for calculating the objective function $\Psi_{\varepsilon, \kappa}$ and its gradient, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
Furthermore, Screenkhorn consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
The second is a constrained LBFGS for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
LBFGS handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of Screenkhorn.
